---
title: "05_result_cross"
author: "Randy"
date: "12/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
load("stan_fev_time1_20201205.Rdata")
launch_shinystan(stan_fev_time1)

load("stan_fev0_20201208.Rdata")
launch_shinystan(stan_fev0)
```


## Negative Binomial without covariance
the data is in long form
counting ~ -1  + age + genotype + gender + Species + 
           (1|SID) + (1|Species) + offset(log(root))),
      data = count_gather,
      family = negbinomial("log")
```{r}
result_nb0 <-
  brms::posterior_summary(stan_nb0, 
                          pars = c("^b_", "^sd_", "sigma"), 
                          probs = c(0.025, 0.975)) %>%
  as.data.frame() %>%
  rownames_to_column("Variable") %>%
  select(-`Q2.5`, -`Q97.5`) %>%
  mutate(wald = abs(Estimate/Est.Error),
         pval = 2 * pnorm(wald, lower.tail = F)) %>%
  column_to_rownames("Variable") %>%
  round(4)

loo_nb0 <- loo::loo(stan_nb0, 
                    save_psis = TRUE)


result_nb0
loo_nb0
waic(stan_nb0)
```

```{r fig.height=10, fig.width=6}
bayesplot::color_scheme_set("viridisD")
plot_fev_time1 <- plot(stan_nb0, 
                       combo = c("dens_overlay", "trace"),
                       theme = ggplot2::theme_bw(base_size = 16) +
                         ggplot2::theme(legend.position = "none"))
```


```{r}
plot(loo_nb0, label_points = TRUE)
pp_check(stan_nb0, nsamples = 1000, type = "stat_2d") + 
  theme_bw(base_size = 20)

# yrep <- brms::posterior_predict(stan_nb0)
# ppc_loo_pit_overlay(count_gather$counting, 
#                     yrep, 
#                     lw = weights(loo_nb0$psis_object), 
#                     compare = "uniform")

pp_check(stan_nb0, nsamples = 100) %>% 
  .$data %>% 
  mutate(value = value + 0.01) %>%
  ggplot(data = ., aes(x = value,  group = rep_id)) +
  geom_line(stat = "density",
            aes(color = if_else(is_y_label == "italic(y)",
                                "Real Data", "Sampled PP")),
            alpha = 0.4) +
  scale_x_log10(name = "not sure what will be x", expand = c(0, 0)) +
  scale_y_continuous(name = "Density", expand = c(0, 0)) +
  scale_color_manual(name = "", values = c("red", "grey")) + 
  theme_classic() +
  ggtitle("counting")
```




## fevslope model no species
fevslope ~ -1 + age + genotype + gender + elast,
      data = fev_ra_time1,
      family = gaussian()
```{r}
result_fev0 <-
  brms::posterior_summary(stan_fev0, 
                          pars = c("^b_", "^sd_", "sigma"), 
                          probs = c(0.025, 0.975)) %>%
  as.data.frame() %>%
  rownames_to_column("Variable") %>%
  select(-`Q2.5`, -`Q97.5`) %>%
  mutate(wald = abs(Estimate/Est.Error),
         pval = 2 * pnorm(wald, lower.tail = F)) %>%
  column_to_rownames("Variable") %>%
  round(4)

loo_fev0 <- loo::loo(stan_fev0, save_psis = TRUE)

waic(stan_fev0)
loo_fev0
result_fev0
```


```{r fig.height=10, fig.width=6}
bayesplot::color_scheme_set("viridisD")
plot(stan_fev0, 
     combo = c("dens_overlay", "trace"),
     theme = ggplot2::theme_bw(base_size = 16) +
       ggplot2::theme(legend.position = "none"))
```


```{r}
plot(loo_fev0, label_points = TRUE)
pp_check(stan_fev0, nsamples = 1000, type = "stat_2d") + 
  theme_bw(base_size = 20)

yrep <- brms::posterior_predict(stan_fev0)
ppc_loo_pit_overlay(fev_ra_time1$fevslope, 
                    yrep, 
                    lw = weights(loo_fev0$psis_object), 
                    compare = "uniform")

pp_check(stan_fev0, nsamples = 100) %>% 
  .$data %>% 
  mutate(value = value + 0.01) %>%
  ggplot(data = ., aes(x = value,  group = rep_id)) +
  geom_line(stat = "density",
            aes(color = if_else(is_y_label == "italic(y)",
                                "Real Data", "Sampled PP")),
            alpha = 0.4) +
  scale_x_continuous(name = "not sure what will be x", expand = c(0, 0)) +
  scale_y_continuous(name = "Density", expand = c(0, 0)) +
  scale_color_manual(name = "", values = c("red", "grey")) + 
  theme_classic() +
  ggtitle("fevslope first time point")
```



## fevslope with species
fevslope ~ age + genotype + gender + il1 +
         Prevotella + Gemella + Staphylococcus + 
         Streptococcus + Veillonella + Leptotrichia + Inquilinus +
         Achromobacter + Neisseria + Lysobacter + 
         Haemophilus + Pseudomonasplus + Stenotrophomonas,
      data = fev_ra_time1,
      family = gaussian()
```{r}
result_fev_time1 <-
  brms::posterior_summary(stan_fev_time1, 
                          pars = c("^b_", "^sd_", "sigma"), 
                          probs = c(0.025, 0.975)) %>%
  as.data.frame() %>%
  rownames_to_column("Variable") %>%
  select(-`Q2.5`, -`Q97.5`) %>%
  mutate(wald = abs(Estimate/Est.Error),
         pval = 2 * pnorm(wald, lower.tail = F)) %>%
  column_to_rownames("Variable") %>%
  round(4)
loo_fev_time1 <- loo::loo(stan_fev_time1, save_psis = TRUE)

loo_fev_time1
result_fev_time1
waic(stan_fev_time1)
```



```{r fig.height=10, fig.width=6}
bayesplot::color_scheme_set("viridisB")
plot_fev_time1 <- plot(stan_fev_time1, 
                       combo = c("dens_overlay", "trace"),
                       theme = ggplot2::theme_bw(base_size = 16) +
                         ggplot2::theme(legend.position = "none"))
```


```{r}
plot(loo_fev_time1, label_points = TRUE)
pp_check(stan_fev_time1, nsamples = 1000, type = "stat_2d") + 
  theme_bw(base_size = 20)

yrep <- brms::posterior_predict(stan_fev_time1)
ppc_loo_pit_overlay(fev_ra_time1$fevslope, 
                    yrep, 
                    lw = weights(loo_fev_time1$psis_object), 
                    compare = "uniform")

pp_check(stan_fev_time1, nsamples = 500) %>% 
  .$data %>% 
  mutate(value = value + 0.01) %>%
  ggplot(data = ., aes(x = value,  group = rep_id)) +
  geom_line(stat = "density",
            aes(color = if_else(is_y_label == "italic(y)",
                                "Real Data", "Sampled PP")),
            alpha = 0.4) +
  scale_x_continuous(name = "not sure what will be x", expand = c(0, 0)) +
  scale_y_continuous(name = "Density", expand = c(0, 0)) +
  scale_color_manual(name = "", values = c("red", "grey")) + 
  theme_classic() +
  ggtitle("fevslope first time point")
```






